\plaintitle

### 2016-09-21 drafts/labor/discussion.tex
turning enumerate into paragraphs

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
\begin{enumerate}
  \item The past isn't a perfect indicator of the future
  \item ``it would be wrong to conclude that
        in the realm of digital labor
        there is nothing new under the sun''
        \cite{scholz2012digital}.
  \item Digital sites of labor are so radically different
        (for many of the reasons that \DO
        articulated in the discussion about
        organizing people and the challenges therein
        \cite{dynamo}, as well as for
        many of the rhizomatic features \citeauthor{miller2011understanding}
        discusses
        \cite{miller2011understanding}).
\end{enumerate}

>>>>

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \cite{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''
\cite{scholz2012digital}.
Many of the challenges that \DO~overcame
--- determining trustworthiness, ensuring anonymity, etc\dots
\cite{dynamo} ---
were relatively unique challenges precipitated by the affordances of the Internet, specifically
that people could (and often do) contribute to communities in a one--off manner
\cite{mcinnis2016one}.
The Internet seemed to make this kind of loose affiliation feasible where before it wasn't
\cite{catalyst,dynamo}.
% articulated in the discussion about
% organizing people and the challenges therein
% \cite{dynamo}, as well as for
% many of the rhizomatic features \citeauthor{miller2011understanding}
% discusses
% \cite{miller2011understanding}).

But this does not mean that
attempting to draw meaningfully from historical scholarship would be folly;
as we have shown in the preceding sections,
enough of piecework can and does inform crowdsourcing that
we should take this as a cue to look first for
historical framings on phenomena that we encounter,
as this work can outline both the mechanisms that we should expect to play out
as well as one of the (perhaps many) possible futures.

In particular, the predictions that have emerged surrounding crowd work have run the spectrum
from deep pessimism to exuberant optimism. \ali{should I cite this?}
In the next section, we will use
the piecework foundation which informed our case studies
to trace out possible Dystopian and Utopian futures for crowd work.
